---
title: "p8105_hw5_nkr2121"
author: "Nihaal Rahman"
output: github_document
---

#Problem 2

Using the list.files function to create the initial data frame
```{r}
names = list.files("data", full.names = TRUE)

data = map(names, ~read_csv(.x) |> 
             mutate(file_name = .x)) |>
             bind_rows()
```

Now cleaning up the data frame
```{r data cleaning }
data_tidy = data |>
  separate(file_name, into = c("folder", "name"), sep = "/") |> 
  separate(name, into = c("arm", "id"), sep = "_") |> 
  separate(id, into = c("subject_id", "csv"), sep = "\\.") |> 
  select(-folder, -csv) |>
  pivot_longer(col = 1:8, names_to = "week", values_to = "value") |> 
  mutate(week = as.numeric(str_extract(week, "\\d+")))
```

Now creating a spaghetti plot
```{r}
figure = ggplot(data_tidy, aes(x = week, y = value, group = subject_id, color = subject_id))+
  geom_point()+
  geom_line()+
  facet_wrap(~arm)+
  labs(title = "Plot of Observations Over Time",
       x = "Week",
       y = "Value")

figure
```

Looking at the two plots, we can see a distinct difference between the control and observation group. The control group seems to be relatively constant across the 8 week period, hovering at roughly 1.25 on average throughout. However, the experimental group demonstrates an upward trend as time progresses, ending around an average of 5.0, roughly. 
